### 2025-03-26 Chapters/Chapter2.tex
Added a couple of data figures in c2 and added text.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/station_heights.png}
    \caption[Distribution of weather station heights above see level]{Distribution of ...}
    \label{fig:station_heights}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/station_heights.png}
    \caption[Distribution of weather station heights above sea level]{Distribution of heights of weather stations above sea level. One station has been excluded as an outlier of well above 1000 meters, having few and inconsistent datapoints.}
    \label{fig:station_heights}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{Figures/gust_factor_2025.png}
    \caption[Distribution of gust factors]{Histogram of gust factors. By definition the lower bound of gust factor is 1. The majority of observed gust factors fall in the range 1.2 to 2. Gust factor decreases with increasing wind speed.}
    \label{fig:gust_factors}
\end{figure}
